Memory for television episodes preserves event content while introducing new across-event similarities

### 2020-02-04 paper/main.tex
updates to methods, results sections for new precision and distinctiveness figs

\begin{figure}[tp]
  \centering
  \includegraphics[width=1\textwidth]{figs/list_learning}
  \caption{\small \textbf{Naturalistic extensions of classic list-learning memory analyses.} \textbf{A.} The probability of first recall as a function of the serial position of the event in the video. \textbf{B}.  The probability of recalling each event, conditioned on having most recently recalled the event \textit{lag} events away in the video.  \textbf{C.} The proportion of participants who recalled each event, as a function of the serial position of the events in the video.  All panels: error bars denote bootstrap-estimated standard error of the mean.}
  \label{fig:list-learning}
\end{figure}

@@

\begin{figure}[tp]
  \centering
  \includegraphics[width=1\textwidth]{figs/precision_distinctiveness}
  \caption{\small \textbf{Novel content-based metrics of naturalistic memory: precision and distinctiveness.} \textbf{A.} The video-recall correlation matrix for a representative participant (17).  The yellow boxes highlight the maximum correlation in each column.  The example participant's overall precision score was computed as the average across correlation values in the yellow boxes.  Their distinctiveness score was computed as the the average (over recall events) of 1 minus the average correlation between each recall event and all other recall events that do not display a box in the same row.  \textbf{B.} The (Pearson's) correlation between precision and hand-annotated memory performance. \textbf{C.} The correlation between distinctiveness and hand-annotated memory performance. \textbf{D.} The correlation between precision and the number of events recovered by the model ($k$). \textbf{E.} The correlation between distinctiveness and the number of events recovered by the model ($k$).}
  \label{fig:precision-distinctiveness}
\end{figure}

\begin{figure}[tp]
  \centering
  \includegraphics[width=1\textwidth]{figs/precision_detail}
  \caption{\small \textbf{Precision metric reflects completeness of recall.} \textbf{A.} Recall precision distributions over participants, for each video event.  Grey violin plots display kernel density estimates for the distribution of recall precision scores for a single video event.  Colored dots within the violin plots represent individual participants' recall precision for that event.  Video events are ordered along the $x$-axis by the average precision with which they were remembered.  \textbf{B.} The set of ``Narrative Details" video annotations (generated by \citealp{ChenEtal17}) for scenes comprising an example video event (22) identified by the HMM.  Each action or feature is highlighted in a different color.  \textbf{C.} A subset of the sentences comprising the most precise (P17) and least precise (P6) participants' recalls of video event 22.  Descriptions of specific actions or features reflecting those highlighted in panel B are highlighted in the corresponding color.}
  \label{fig:precision-detail}
\end{figure}

\begin{figure}[tp]
  \centering
  \includegraphics[width=1\textwidth]{figs/distinctiveness_detail}
  \caption{\small \textbf{Distinctiveness metric reflects specificity of recall.} \textbf{A.} Recall distinctiveness distributions over participants, for each video event.  Kernel density estimates for each video event's distribution of recall distinctiveness scores, analogous to Fig.~\ref{fig:precision-detail}A.  \textbf{B.} The set of ``Narrative Details" video annotations (generated by \citealp{ChenEtal17}) for scenes comprising an example video event (19) identified by the HMM.  \textbf{C.} The sentences comprising the most distinctive (P13) and least distinctive (P11) participants' recalls of video event 19.  Descriptions of recalled content specific to video event 19 (as opposed to that combining surrounding events) are highlighted.}
  \label{fig:distinctiveness-detail}
\end{figure}

Further intuition for the behaviors captured by these two metrics may be gained by directly examining the content of the video and recalls our framework models.  In Figure \ref{fig:precision-detail}, we contrast recalls for the same video event from two participants: one with a high precision score (P17), the other with a low precision score (P6).  From the HMM-identified event boundaries, we recovered the set of annotations describing the content of an example video event (event 22; Fig.~\ref{fig:precision-detail}B), and divided them into different color-coded sections for each action or feature described.  We then similarly recovered the set of sentences comprising the corresponding recall event for each of the two example participants.  Because the recall sliding windows overlap heavily, and each recall event spans multiple recall timepoints (i.e., windows), we have stripped any sentences from the beginning and end that describe earlier or later video events for the sake of readability.  In other words, Fig.~\ref{fig:precision-detail}C shows a subset of the full recall event text, comprising sentences between the first and last descriptions of content from the example video event.  We then colored all words describing actions and features coded in panel B by their corresponding color.  Visual comparison of the transcripts reveals that the most precise participant's recall captures a greater amount of the video event's content, and with far more detail.

Figure \ref{fig:distinctiveness-detail} similarly contrasts two participants' recall for an example video event (event 19) to illustrate the tangible differences between high and low distinctiveness scores.  Here, we have extracted the full text from the most

>>>>

\begin{figure}[t]
  \centering
  \includegraphics[width=1\textwidth]{figs/list_learning}
  \caption{\small \textbf{Naturalistic extensions of classic list-learning memory analyses.} \textbf{A.} The probability of first recall as a function of the serial position of the event in the video. \textbf{B}.  The probability of recalling each event, conditioned on having most recently recalled the event \textit{lag} events away in the video.  \textbf{C.} The proportion of participants who recalled each event, as a function of the serial position of the events in the video.  All panels: error bars denote bootstrap-estimated standard error of the mean.}
  \label{fig:list-learning}
\end{figure}

\begin{figure}[t]
  \centering
  \includegraphics[width=1\textwidth]{figs/precision_distinctiveness}
  \caption{\small \textbf{Novel content-based metrics of naturalistic memory: precision and distinctiveness.} \textbf{A.} The video-recall correlation matrix for a representative participant (17).  The yellow boxes highlight the maximum correlation in each column.  The example participant's overall precision score was computed as the average across correlation values in the yellow boxes.  Their distinctiveness score was computed as the the average (over recall events) of 1 minus the average correlation between each recall event and all other recall events that do not display a box in the same row.  \textbf{B.} The (Pearson's) correlation between precision and hand-annotated memory performance. \textbf{C.} The correlation between distinctiveness and hand-annotated memory performance. \textbf{D.} The correlation between precision and the number of events recovered by the model ($k$). \textbf{E.} The correlation between distinctiveness and the number of events recovered by the model ($k$).}
  \label{fig:precision-distinctiveness}
\end{figure}

@@

\begin{figure}[t]
  \centering
  \includegraphics[width=1\textwidth]{figs/precision_detail}
  \caption{\small \textbf{Precision metric reflects completeness of recall.} \textbf{A.} Recall precision distributions over participants, for each video event.  Grey violin plots display kernel density estimates for the distribution of recall precision scores for a single video event.  Colored dots within the violin plots represent individual participants' recall precision for that event.  Video events are ordered along the $x$-axis by the average precision with which they were remembered.  \textbf{B.} The set of ``Narrative Details" video annotations (generated by \citealp{ChenEtal17}) for scenes comprising an example video event (22) identified by the HMM.  Each action or feature is highlighted in a different color.  \textbf{C.} A subset of the sentences comprising the most precise (P17) and least precise (P6) participants' recalls of video event 22.  Descriptions of specific actions or features reflecting those highlighted in panel B are highlighted in the corresponding color.}
  \label{fig:precision-detail}
\end{figure}

\begin{figure}[t]
  \centering
  \includegraphics[width=1\textwidth]{figs/distinctiveness_detail}
  \caption{\small \textbf{Distinctiveness metric reflects specificity of recall.} \textbf{A.} Recall distinctiveness distributions over participants, for each video event.  Kernel density estimates for each video event's distribution of recall distinctiveness scores, analogous to Fig.~\ref{fig:precision-detail}A.  \textbf{B.} The set of ``Narrative Details" video annotations (generated by \citealp{ChenEtal17}) for scenes comprising an example video event (19) identified by the HMM.  \textbf{C.} The sentences comprising the most distinctive (P13) and least distinctive (P11) participants' recalls of video event 19.  Descriptions of recalled content specific to video event 19 (as opposed to that combining surrounding events) are highlighted.}
  \label{fig:distinctiveness-detail}
\end{figure}

Further intuition for the behaviors captured by these two metrics may be gained by directly examining the content of the video and recalls our framework models.  In Figure \ref{fig:precision-detail}, we contrast recalls for the same video event (event 22) from two participants: one with a high precision score (P17), the other with a low precision score (P6).  From the HMM-identified event boundaries, we recovered the set of annotations describing the content of an example video event (Fig.~\ref{fig:precision-detail}B), and divided them into different color-coded sections for each action or feature described.  We then similarly recovered the set of sentences comprising the corresponding recall event for each of the two example participants.  Because the recall sliding windows overlap heavily, and each recall event spans multiple recall timepoints (i.e., windows), we have stripped any sentences from the beginning and end that describe earlier or later video events for the sake of readability.  In other words, Fig.~\ref{fig:precision-detail}C shows a subset of the full recall event text, comprising sentences between the first and last descriptions of content from the example video event.  We then colored all words describing actions and features coded in panel B by their corresponding color.  Visual comparison of the transcripts reveals that the most precise participant's recall both captures more of the video event's content, and does so with far more detail.

Figure \ref{fig:distinctiveness-detail} similarly contrasts two example participants' recalls for a common video event (event 19) to illustrate the tangible differences between high and low distinctiveness scores.  Here, we have extracted the full set of sentences comprising the most distinctive recall event (P13) and least distinctive recall event (P11) recall event matched to the example video event (Fig.~\ref{fig:distinctiveness-detail}C).  We also extracted the annotations for the example video event, as well as those from each other video event whose content the example participants' single recall events described (Fig.~\ref{fig:distinctiveness-detail}B).  We then shaded the annotation text for each video event with a different color, and shaded each word of the example participants' recall text by the color of the video event it describes.  The majority of the most distinctive recall event text describes video event 19's content, with the first five and last one sentence describing the video events immediately preceding and succeeding the current one, respectively.  Meanwhile, the least precise participant's recall for video event 19 blends the content from five separate video events, does not transition between them in order, and often combines descriptions of two video events' content in the same sentence
